A Switching Planner for Combined Task and Observation Planning

### 2010-11-30 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/evaluation.tex
The graphs need updating!
new discussion section

We perform experiments on tasks of several sizes. The objective is to
find one or more objects and report their position to the user. In
order to determine the impact of the reliability of sensing in a
comparison with the baseline, we run tests on identical problems but
changed the sensor model for the target objects: the probability for
perceiving the object if it was there went from 0.9 in the easiest
case to 0.65 and 0.4 in the average and hard cases respectively. In
addition, we test how our system performs in tasks requiring indirect
sensing. Here, we gave the planner rewards for visiting a certain type
of room (e.g. kitchen or office). We did not place any humans in those
scenarios, so the only way of determining the room category is by
looking for objects typical for that room type. As this indirect
reasoning is a tasks that cannot be performed by the continual planner
alone, we did not run the baseline system on those problems.

In our evaluation we run 50 simulations in each configuration. A run
timeouts after 30 minutes (1800 seconds). The planning and simulation
models are in exact correspondence. Not all problems have a solution,
so we also examine whether or not detection of the non-existence of a
solution is important in stochastic domains.
%% 
We perform multiple tests with different limits for the
belief-space size in contingent sessions.  Higher limits result in
longer contingent planning times and higher plan quality.

Using a satisficing, optimistic serial planner in sequential sessions
makes optimising for the expected reward difficult. Only reasoning
about single traces, it is optimistic wrt the remaining costs to a
goal and pessimistic regarding the probability of reaching it. By
setting the rewards to non-extremal values has little effect on that
system. Therefore, we do not consider expected utility in our
experiments. Instead, we report average costs of the plans and the
success rate (as a ratio between solved and solvable problems).

\begin{figure}[h!]
  % \centering
  % \includegraphics{dora1-time}\hfill
  % \vspace{2mm}
  \includegraphics{dora2-time}\hfill
  \vspace{2mm}
  \includegraphics{dora3-time}\hfill
  \vspace{2mm}
  \includegraphics{dora4-time}\hfill
  \vspace{2mm}
  \includegraphics{dora56-time}\hfill
  \vspace{2mm}
  \includegraphics{dora-cat-time}\hfill
  \caption{Average runtime}
  \label{fig:results-time}
\end{figure}

\begin{figure}[h!]
  % \centering
  % \includegraphics{dora1-quality}\hfill
  % \vspace{2mm}
  \includegraphics{dora2-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora3-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora4-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora56-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora-cat-quality}\hfill
  \caption{Average plan costs and number of successful runs.}
  \label{fig:results-quality}
\end{figure}

@@

Our experimental results are summarised in
Figure~\ref{fig:results-time} and Figure~\ref{fig:results-quality}. We
find that the time spent on contingent planning increases steeply as
the abstraction $\bstate_0$ becomes more refined. For coarse initial
configurations, the cost of contingent planning is compensated by the
decrease of time spent in Fast Downward. Addressing success ratios and
plan costs, for objects that can be easily detected there is little
gain in using a decision-theoretic planner, as the greedy sensing
approach by the baseline is sufficient. With decreasing sensor
reliability contingent planning pays off.%% : while the resulting plans are still
%% longer on average, the impact on the number of solved tasks was much
%% smaller than for the baseline system.  Less aggressive abstraction
of the initial configuration results in longer runtimes. In our
scenario it is worthwhile being assumptively aggressive.  We suppose
the relatively high success rate irrespective of the coarseness of the
initial configuration indicates the effectiveness of using conditional
entropy to guide abstraction refinement.

We find that abstraction has little impact on plan
costs and success rate in our scenario. Increasing the size of the
initial abstract belief beyond 50 states rarely pays off, because
while additional information may facilitate better plans, the indirect
sensing tests report the same result. Here, we only really see an
impact in terms of the runtime of contingent planning.

>>>>

We evaluated our switching planner against the baseline in several
problems with the number of rooms ranging from 3 to 6. We examine the
impact of sensing reliability, experimenting using sensor models that
are: ({\em reliable}) $0.9$ chance the object is perceived if it is
present, ({\em semi-reliable}) chance is 0.65, and ({\em noisy})
chance is 0.4. The continual planning times are reported in
Figure~\ref{fig:results-time}, and the quality data in
Figure~\ref{fig:results-quality}. Here, in switching runs we examine
the performance of our system where $b_0$ allocates non-zero
probability to between 20 and 200 abstract states during contingent
sessions. For Items~$a$-$e$ the objective is to find one or more
objects and report their position to the user. In some of the tasks we
configured the environment so that no plan exists, by excluding the
desired object from the environment. Item~$f$ reports for tasks
requiring indirect sensing, where the robot must relocate to a
particular room category. For Item~$f$ there is no human in the
environment, and therefore the baseline cannot be used, because there
are no sensing schemata that directly sense room categories. In our
evaluation we run 50 simulations in each configuration, and have a
timeout on each simulation 30 minutes (1800 seconds). In our domain,
rewards encapsulate a goal condition, and therefore we find it
intuitive to report average costs of the plans and the success rate in
problems that admit a solution (i.e., positive reward scaled by a
constant factor).

%% Because the switching utility model

%% Using a satisficing, optimistic serial planner in sequential sessions
%% makes optimising for the expected reward difficult. Only reasoning
%% about single traces, it is optimistic wrt the remaining costs to a
%% goal and pessimistic regarding the probability of reaching it. By
%% setting the rewards to non-extremal values has little effect on that
%% system. Therefore, we do not consider expected utility in our
%% experiments. Instead, we report average costs of the plans and the
%% success rate (as a ratio between solved and solvable problems).

\begin{figure}[h!]
  % \centering
  % \includegraphics{dora1-time}\hfill
  % \vspace{2mm}
  \includegraphics{dora2-time}\hfill
  % \vspace{2mm}
  \includegraphics{dora3-time}\hfill
  % \vspace{2mm}
  \includegraphics{dora4-time}\hfill
  \vspace{2mm}
  \includegraphics{dora56-time}\hfill
  \vspace{2mm}
  \includegraphics{dora-cat-time}\hfill
  \caption{Average runtime}
  \label{fig:results-time}
\end{figure}

\begin{figure}[h!]
  % \centering
  % \includegraphics{dora1-quality}\hfill
  % \vspace{2mm}
  \includegraphics{dora2-quality}\hfill
  % \vspace{2mm}
  \includegraphics{dora3-quality}\hfill
  % \vspace{2mm}
  \includegraphics{dora4-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora56-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora-cat-quality}\hfill
  \caption{Average plan costs and number of successful runs.}
  \label{fig:results-quality}
\end{figure}

@@

Examining success ratios and plan costs, where sensing is reliable
there is little to be gained by using the contingent planner, as the
greedy sensing approach of the baseline is sufficient. Not
surprisingly, as sensing degrades contingent planning pays off.  Also,
we find that time spent in contingent planning increases steeply as
the abstraction $\bstate_0$ becomes more refined.  That refinement
seems to be paying off in terms of the success ratio, particularly for
problems $d$ and $e$, where we had sequential sessions using weighted
$A^*$ (rather than $A^*$). For less refined initial configurations, the
increase cost of contingent planning is compensated by a decrease in
time spent executing the serial system Fast Downward. The relatively
high success rate irrespective of the level of refinement in the
initial configuration indicates the effectiveness of using conditional
entropy to guide abstraction refinement in our setting.

%% :
%%while the resulting plans are still
%% longer on average, the impact on the number of solved tasks was much
%% smaller than for the baseline system.

%% Less aggressive abstraction of the initial configuration results in
%% longer runtimes, with little to be gained in terms of plan quality. We
%% conclude that in our scenario it is worthwhile being assumptively
%% aggressive.

%% We find that abstraction has little impact on plan
%% costs and success rate in our scenario. Increasing the size of the
%% initial abstract belief beyond 50 states rarely pays off, because
%% while additional information may facilitate better plans, the indirect
%% sensing tests report the same result. Here, we only really see an
%% impact in terms of the runtime of contingent planning.
